Fig1

### 2020-08-07 analysis/03_datawrangling.Rmd
pca and some candidate now suppl fig 1

literaturegenes <- c(curleychampagnegenes, 
                     "VIP", "GNIH", "GAL", "TH", "THRB",
                     "GNRHR", "GNRH1", "CGNRH-R", "FSHB", "FSHR")
literaturegenes

>>>>

datadrivengenes <- c("COX1", "COX2", "CYTB", "ATP2B4", "LOC107055658", 
                     "CHGA", "TF", "OVALY", "ANXA5")

literaturegenes <- c(curleychampagnegenes, datadrivengenes,
                     "VIP", "GNIH", "GAL", "TH", "THRB",
                     "GNRHR", "GNRH1", "CGNRH-R", "FSHB", "FSHR")
literaturegenes

### 2020-08-07 analysis/boneyard.Rmd
pca and some candidate now suppl fig 1

>>>>

```{r}
## prlpit
PRLpit <- candidatevsd %>% 
  filter(gene == "PRL", tissue == "pituitary")

# list of pvalue and DEGs
allDEG <- read_csv("../results/06_allDEG.csv")  %>%
  mutate(direction = factor(direction, levels = hypothesislevels))

# DEGs infor for PRL and external
hilodf <- allDEG %>%
  filter(comparison == "lo_hi")  %>%
  arrange(padj) 
hilogenes <- hilodf %>%  top_n(20) %>% pull(gene)

eggchickdf <- allDEG %>%
  filter(!comparison %in% c("lo_hi", "nest_eggs", "nest_chicks"))  %>%
  arrange(padj)  
eggchickgenes <- eggchickdf %>%  top_n(20) %>% pull(gene)

## data-driven PRL genes
pithilo <- makecorrdf("female", "pituitary", hilogenes)
pitWGCNA <- makecorrdf("female", "pituitary", WGCNAgenes[32:52])

## https://www.gynecologiconcology-online.net/article/S0090-8258(19)30069-1/fulltext
cancergenes <- makecorrdf("female", "pituitary", c(shaidgenes,suszynskaagenes, "PRL"))

## for scatter correlation (not currently usesed)
candidatevsdwide <- candidatevsd  %>%
    pivot_wider(names_from = gene, values_from = counts) 
pitwide <- subsetcandidatevsdwide(sexlevels, "pituitary")

## number of genes total vs plotted

eggchickdf %>% filter(tissue == "pituitary") %>% nrow()
hilodf %>% filter(tissue == "pituitary") %>% nrow()
length(WGCNAgenes)

b1 <- png::readPNG("../figures/images/fig_fig3b.png")
b1 <- ggdraw() +  draw_image(b1, scale = 1)

b2 <- makenewbargraph("pituitary", "female","eggs_chicks", 0, 4000) + labs(subtitle = "female")  + labs(title = " ") +
  scale_x_discrete(labels = "eggs vs. chicks")
b3 <- makenewbargraph("pituitary", "male", "eggs_chicks", 0, 4000)  + labs(subtitle = "male")  + labs(title = " ") +
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank()) +
  scale_x_discrete(labels = "eggs vs. chicks")
b4 <- makenewbargraph("pituitary", "male", "lo_hi", 0, 4000)  +
  scale_x_discrete(labels = "lo vs. hi PRL")
b5 <- makenewbargraph("pituitary", "female", "lo_hi", 0, 4000)   + 
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank(), 
        axis.text.y = element_blank(), axis.line.y = element_blank()) +
  scale_x_discrete(labels = "lo vs. hi PRL")
b25 <- plot_grid(b2,b3,b4,b5, nrow = 2, rel_widths = c(1.2,1), rel_heights = c(1.2,1))

b6 <-  plottopDEGs(eggchickdf, "female",  "LFC eggs vs. chicks", "Top 10 female DEGs") + labs(title = " ")
b7 <-  plottopDEGs(eggchickdf, "male",  "LFC eggs vs. chicks", "Top 10 male DEGs") + labs(title = " ")
b8 <-  plottopDEGs(hilodf, "female",  "LFC lo vs. hi PRL", NULL)
b9 <-  plottopDEGs(hilodf, "male",  "LFC lo vs. hi PRL", NULL)
b15 <- plot_grid(b1,b25,nrow = 1, rel_widths = c(1.2,1))
b69 <- plot_grid(b6,b7,b8,b9, align = "v" , rel_heights = c(1.2,1))
b <- plot_grid(b15,b69, labels = c("C"), label_size = 8, rel_widths = c(1.2,1))

c1 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 DEGs, low vs. high PRL") 
c2 <- plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes in WGCNA module with PRL") 
c3 <- plotcorrplot(cancergenes, NULL) + theme(legend.position = "right") + labs(subtitle = "Breast, ovary, & piuitary cancer genes", color = "Correlation")
c <- plot_grid(c1,c2,c3, nrow = 1, labels = c("D"), label_size = 8, rel_widths = c(1,1,1.3))

fig3 <- plot_grid(a, b, c, nrow = 3, rel_heights = c(1.2,2,1.8))
fig3
```

### 2020-08-07 analysis/figure-1.Rmd
pca and some candidate now suppl fig 1

@@

png("../figures/fig1-1.png", width = 7, height = 4.5, 
    units = 'in', res = 300)
plot(fig1) # Make plot
dev.off()

>>>>

## Supplemental PCA data

```{r}
# pca relies on count data from limma
pca_h1 <- subsetmakepca("hypothalamus", alllevels, sexlevels)	
pca_h2 <- makefvizdf("hypothalamus", alllevels, sexlevels)

pca_p1 <- subsetmakepca("pituitary", alllevels, sexlevels)	
pca_p2 <- makefvizdf("pituitary", alllevels, sexlevels)

pca_g1 <- subsetmakepca("gonads", alllevels, sexlevels)	
pca_g2 <- makefvizdf("gonads", alllevels, sexlevels)	
```

## Supplemental Data-driven genes vsds for box plots

```{r candidates}
# genes lists in "./analysis/03_datawrangling.Rmd" and old lists in "./R/genelists.R"

candidatevsd <- read_csv("../results/03_candidatevsd.csv") %>% 
  select(-X1) %>%
  filter(treatment %in% alllevels) %>%
  mutate(treatment = factor(treatment, levels = charlevels)) %>%
  drop_na() 
head(candidatevsd)
```

## Fig 3

```{r supplfig, fig.height=7.25, fig.width=7.25}

a <- plotpc12(pca_h1, pca_h2, pca_h1$treatment, allcolors, "Hypothalamus", NULL) 
c <- plotpc12(pca_p1, pca_p2, pca_p1$treatment, allcolors, "Pituitary", NULL) 
e <- plotpc12(pca_g1, pca_g2, pca_g1$treatment, allcolors, "Gonads", NULL)

b1 <- fviz_screeplot(pca_h2, addlabels = F, barfill = "grey", barcolor = "grey") +
  theme_B3() + labs(title = " ")
d1 <- fviz_screeplot(pca_p2, addlabels = F, barfill = "grey", barcolor = "grey") +
  theme_B3() + labs(title = " ")
f1 <- fviz_screeplot(pca_g2, addlabels = F, barfill = "grey", barcolor = "grey") +
  theme_B3() + labs(title = " ")

b2 <- candidateboxplot("hypothalamus", c("COX1"), sexlevels)
d2 <- candidateboxplot("pituitary", c("PRL"), sexlevels)
f2 <- candidateboxplot("gonad", c("OVALY"), sexlevels)

supplfig <- plot_grid(a,b1,b2, c,d1,d2,e,f1,f2, nrow = 3, rel_widths = c(2,1,2))
```

@@

png("../figures/fig1-1.png", width = 7, height = 4.5, 
    units = 'in', res = 300)
plot(fig1) 
dev.off()

pdf(file="../figures/supplfig-1.pdf", width=7.5, height=7.5)
plot(supplfig)
dev.off()

png("../figures/supplfig-1.png", width = 7.5, height = 7.5, 
    units = 'in', res = 300)
plot(supplfig)  
dev.off()
